|

### 2020-02-02 paper/cogsci/paper_jan28.Rmd
changed Fig 3 figure legend, minor edits, condensed refs

With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.  Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage. To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1). In prior work with egocentric videos, [@sanchez2018postural] OpenPose performed comparably to other detectors specified for detecting only faces.

@@

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_detect),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_detect)) + 
  geom_smooth(data = wide_cropped, aes(weight = num_detect),
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = wide_gold, aes(weight = num_detect),
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

How does variability across different contexts influence the social information in the infant view? Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in. Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all p<.001, see accompanying codebase]. For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchens (see Figure \ref{fig:DetByLocation}).

@@

Here, we analyzed the social information in view in a dense, longitudinal dataset, applying computer-vision models to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. This analysis has yielded a better understanding of infants' evolving access to social information. We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. However, this finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].

>>>>

With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.  Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage. To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1). In prior work examining egocentric videos, OpenPose performed comparably to other modern face detection models [@sanchez2018postural].

@@

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_detect),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_detect), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  geom_smooth(data = wide_cropped, aes(weight = num_detect), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

How does variability across different contexts influence the social information in the infant view? Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in. Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase]. For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchens (see Figure \ref{fig:DetByLocation}).

@@

Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. This analysis has yielded a better understanding of infants' evolving access to social information. We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. However, this finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
